How to select predictive models for decision-making or causal inference?

### 2023-12-08 how_to_select_causal_models.tex
iter

We first illustrate the problem of causal model selection and briefly review
prior art. Then we anchor causal model selection in the \emph{potential outcome}
framework and details the causal risks and model-selection procedure. We then
rewrite the so-called $R\text{-risk}$, as a reweighted version of mean squared
difference between the true and estimated individualized treatment effect.
Finally, we conduct a thorough empirical study comparing the different metrics
on a wide variety of data-generative processes based on simulations and real
data, going beyond prior work
\citep{schuler_comparison_2018,alaa_validating_2019} (reviewed in Appendix
\ref{apd:prior_work}).

>>>>

We first illustrate the problem of causal model selection and briefly review
prior art. Then we anchor causal model selection in the \emph{potential outcome}
framework and details the causal risks and model-selection procedure. We then
rewrite the so-called $R\text{-risk}$, as a reweighted version of mean squared
difference between the true and estimated individualized treatment effect.
Finally, we conduct a thorough empirical study comparing the different metrics
on a wide variety of data-generative processes based on simulations and real
data, going beyond prior work based on smaller simulation sets
\citep{schuler_comparison_2018,alaa_validating_2019} (Appendix
\ref{apd:prior_work}).
